infer: An R package for tidyverse-friendly statistical inference

### 2021-09-12 figs/paper/paper.tex
refine JOSS paper citations

Several software packages on the Comprehensive R Archive Network share
functionality with \texttt{infer} (R Core Team, 2021). \texttt{broom}
and \texttt{parameters} convert model objects to unified output formats,
though they do not provide methods for fitting models, describing null
distributions, performing bootstrapping, or calculating summary
statistics from tabular data. \texttt{statsexpressions}, and adjacent
packages in the \texttt{easystats} ecosystem, implement wrappers with
consistent interfaces for theory-based hypothesis tests. Similarly,
\texttt{mosaic} is a package used to teach statistics by unifying
summary statistics, visualization, and modeling with a consistent API
built around R's formula interface. The \texttt{mosaic} package also
includes functionality to conduct randomization-based inference. At a
higher level, though, the structure of each of these packages is defined
by model types and statistics, where each model type or statistic has
its own associated function and/or object class. In contrast,
\texttt{infer} is structured around four functions, situating statistics
and model types within a more abstracted grammar.\footnote{This grammar
  follows from Allen Downey's ``there is only one test'' framework
  (Downey, 2016).}

@@

\leavevmode\hypertarget{ref-downey2016}{}%
Downey, A. B. (2016). There is still only one test.

@@

@@

@@

>>>>

Several software packages on the Comprehensive R Archive Network share
functionality with \texttt{infer} (R Core Team, 2021). \texttt{broom}
and \texttt{parameters} convert model objects to unified output formats,
though they do not provide methods for fitting models, describing null
distributions, performing bootstrapping, or calculating summary
statistics from tabular data (Lüdecke, Ben-Shachar, Patil, \& Makowski,
2020; Robinson, Hayes, \& Couch, 2021). \texttt{statsExpressions}, and
adjacent packages in the \texttt{easystats} ecosystem, implement
wrappers with consistent interfaces for theory-based hypothesis tests
(Patil, 2021). Similarly, \texttt{mosaic} is a package used to teach
statistics by unifying summary statistics, visualization, and modeling
with a consistent API built around R's formula interface. The
\texttt{mosaic} package also includes functionality to conduct
randomization-based inference (Pruim, Kaplan, \& Horton, 2017). At a
higher level, though, the structure of each of these packages is defined
by model types and statistics, where each model type or statistic has
its own associated function and/or object class. In contrast,
\texttt{infer} is structured around four functions, situating statistics
and model types within a more abstracted grammar.\footnote{This grammar
  follows from Allen Downey's ``there is only one test'' framework
  (Downey, 2016).}

@@

\leavevmode\hypertarget{ref-downey2016}{}%
Downey, A. B. (2016). There is still only one test. Retrieved from
\url{http://allendowney.blogspot.com/2016/06/there-is-still-only-one-test.html}

@@

\leavevmode\hypertarget{ref-r-parameters}{}%
Lüdecke, D., Ben-Shachar, M. S., Patil, I., \& Makowski, D. (2020).
Extracting, computing and exploring the parameters of statistical models
using {R}. \emph{Journal of Open Source Software}, \emph{5}(53), 2445.
doi:\href{https://doi.org/10.21105/joss.02445}{10.21105/joss.02445}

@@

\leavevmode\hypertarget{ref-r-statsExpressions}{}%
Patil, I. (2021). {statsExpressions: {R} Package for Tidy Dataframes and
Expressions with Statistical Details}. \emph{{Journal of Open Source
Software}}, \emph{6}(61), 3236.
doi:\href{https://doi.org/10.21105/joss.03236}{10.21105/joss.03236}

\leavevmode\hypertarget{ref-r-mosaic}{}%
Pruim, R., Kaplan, D. T., \& Horton, N. J. (2017). The mosaic package:
Helping students to 'think with data' using r. \emph{The R Journal},
\emph{9}(1), 77--102. Retrieved from
\url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}

@@

\leavevmode\hypertarget{ref-r-broom}{}%
Robinson, D., Hayes, A., \& Couch, S. (2021). \emph{Broom: Convert
statistical objects into tidy tibbles}. Retrieved from
\url{https://CRAN.R-project.org/package=broom}
